%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {M. Sc. in Computer Science (Current GPA: 1.0)} % Degree
    {Technical University Berlin} % Institution
    {Berlin, Germany} % Location
    {2017 - 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Specializing in scalable data systems and machine learning.}
        \item{Working as a student researcher beginning with the second semester with a focus on causal learning and data processing on modern hardware.}
        \item{Scholar of the Klaus Murmann Fellowship Program of the Foundation of German Business.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Visiting Undergraduate Student} % Degree
    {Harvard University} % Institution
    {Cambridge, MA, USA} % Location
    {2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Took courses in machine learning, data visualization and economics and computation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Visiting Undergraduate Student} % Degree
    {Massachusetts Institute of Technology} % Institution
    {Cambridge, MA, USA} % Location
    {2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Took a course on entrepreneurship at the MIT Sloan School of Management.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {B.Sc. in Computer Science and Business Management (GPA: 1.4)} % Degree
    {NORDAKADEMIE Hochschule der Wirtschaft} % Institution
    {Elmshorn, Germany} % Location
    {2011 - 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Academic part of the co-op program in cooperation with Otto (GmbH \& Co. KG).}
        \item{Served as Head of Departmental Student Society for Computer Science and Business Management.}
        \item{Received scholarship from the Klaus Murmann Fellowship Program of the Foundation of German Business (SDW).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
