%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Student Assistant at the Data Engineering Systems Group} % Job title
    {Hasso Plattner Institute} % Organization
    {Potsdam, Germany} % Location
    {05/2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Continued working with Prof. Rabl as first hire and assisted with creating the new group.}
      \item{Designing a novel message broker architecture that leverages remote direct memory access and persistent memory as my master thesis. To be presented at \textbf{SIGMOD '20.}}
      \item{Designing and executing benchmark of existing message brokers.}
      \item{Researched approaches to causal discovery and how to bring these concepts into real-world systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Research Assistant at the Database and Information Management Group} % Job title
    {Technical University Berlin} % Organization
    {Berlin, Germany} % Location
    {04/2018 - 04/2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Analyzed the robustness of game-theoretic approaches to inferring influence between senators from their voting behavior and showed high instability of learned parameters with respect to hyperparameters and minor manipulation of the data.}
      \item{Deeply investigated concepts of causality and how to bring causal discovery mechanisms to data systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Engineer} % Job title
    {Project A Ventures} % Organization
    {Berlin, Germany} % Location
    {06/2015 - 09/2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead engineer on a three months project analyzing the balance of a 500+MM USD marketplace. Built data pipelining, a dashboard solution as well as marketing automations based on our findings. This has helped to increase the revenue of the company and intelligently allocate marketing budgets.}
        \item {Designed, implemented and extended data warehouses, large data processing pipelines and data products built on top of those.}
        \item {Analyzed and predicted KPIs by using customer and marketing data.}
        \item{Interviewed and educated new data teams for the ventures.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder} % Job title
    {owlhub. UG} % Organization
    {Hamburg, Germany} % Location
    {01/2014 - 09/2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Co-founded a stock analysis network for the everyday investor.}
      \item{Main responsibilities were around Product, Data and Marketing. Developed the web application in Ruby on Rails.}
      \item{Developed owlhub. Insights dashboard as part of Harvard CS 171 Visualization.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-op Student in Computer Science and Business Management} % Job title
    {Otto (GmbH \& Co. KG)} % Organization
    {Hamburg, Germany} % Location
    {10/2011 - 03/2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {erformed the practical part of the integrated degree program in the form of several internships within Otto Group companies.}
        \item {Internships in the areas of project and product management, software development, venture capital and data science for an average of three months each.}
        \item{Two internships highlighted below:}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Science Intern in Business Intelligence} % Job title
    {otto group} % Organization
    {Hamburg, Germany} % Location
    {11/2014 - 03/2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote bachelor thesis on "Evaluation of Methods for Identifying Brand Names in Search Queries in E-Commerce". Researched methods and helpful metrics for the identification task. Extended existing and implementing new metrics, methods and machine learning algorithms and thereby decreased run-time of existing approach by 75 \%.}
        \item {Test-driven and agile development in Python using various third-party libraries.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
  \cventry
    {Data Science Intern} % Job title
    {Blue Yonder GmbH} % Organization
    {Hamburg, Germany} % Location
    {06/2014 - 08/2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Data science using Python combined with proprietary and open-source libraries.}
        \item {Performed initial data exploration and preparatory model development for a customer project on dynamic pricing in the travel industry. This analysis was the foundation of subsequent negotiations and project scope definitions.}
        \item{Supported creation of a tutorial on data science for external customers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mandatory Civilian Service} % Job title
    {YMCA Youth Center Lemsahl} % Organization
    {Hamburg, Germany} % Location
    {10/2010 - 05/2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led events, youth groups and a summer camp together with teams of volunteers and regular staff.} 
        \item {Supervised and supported volunteers.}
        \item{Supported day-to-day operations of the center and designed web and print media.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
